Mirror, mirror on the wall. Which's the best match of them all?

### 2024-01-19 PNAS/index.Rnw
missed one r

If we begin by considering the multiple comparison problem relative to the minimal $\ell/d$ independent comparisons between a blade cut and a wire, we can compute the overall false positive rate for all comparisons using $r$, the false positive rate for one comparison, and simple probability calculations. Let $$F_n:=\{\text{at least one false pos. in }n\text{ disjoint comparisons}\}.$$ Then, $P(F_1) = e$, $P(\overline{F_1}) = 1-e$, $P(F_n) = [1-e]^n$, and $P(\overline{F_n}) = 1 - \left[P(\overline{F_1})\right]^n$.
% Using this relationship between $F_n$ and the false positive rate $r$, we can determine what $e$ must be in order to limit $P(F_n)$ to an acceptable level by solving for $e$: $e = 1 - \left[1 - P(F_n)\right]^{1/n}$.
\Cref{fig:Accuracy} shows $P(\overline{F_n})$ on the y-axis; if we set 90\% as the acceptable examination-wide false positive rate (FPR), we can make 2 comparisons when the single-comparison FPR is 0.05 and 10 comparisons at 0.01. Thus, at an error rate of \Sexpr{sprintf("%.2f", fpr)}, we can conduct approximately 5 comparisons in the course of an examination without exceeding the examination-wide FPR of 10\%.

>>>>

If we begin by considering the multiple comparison problem relative to the minimal $\ell/d$ independent comparisons between a blade cut and a wire, we can compute the overall false positive rate for all comparisons using $e$, the false positive rate for one comparison, and simple probability calculations. Let $$F_n:=\{\text{at least one false pos. in }n\text{ disjoint comparisons}\}.$$ Then, $P(F_1) = e$, $P(\overline{F_1}) = 1-e$, $P(F_n) = [1-e]^n$, and $P(\overline{F_n}) = 1 - \left[P(\overline{F_1})\right]^n$.
% Using this relationship between $F_n$ and the false positive rate $r$, we can determine what $e$ must be in order to limit $P(F_n)$ to an acceptable level by solving for $e$: $e = 1 - \left[1 - P(F_n)\right]^{1/n}$.
\Cref{fig:Accuracy} shows $P(\overline{F_n})$ on the y-axis; if we set 90\% as the acceptable examination-wide false positive rate (FPR), we can make 2 comparisons when the single-comparison FPR is 0.05 and 10 comparisons at 0.01. Thus, at an error rate of \Sexpr{sprintf("%.2f", fpr)}, we can conduct approximately 5 comparisons in the course of an examination without exceeding the examination-wide FPR of 10\%.
